### 2019-12-28 paper/sex_selection_spacing-ver3.tex
Delete discussion of regions in paper and region appendix

\date{March 2018}

@@

% Demography abstract
\noindent 
Strong son preference is typically associated with shorter birth spacing in the absence of 
sons, but access to sex selection has the potential to reverse this pattern because each 
abortion extends spacing by six to twelve months. 
I introduce an empirical method that simultaneously accounts for how sex selection 
increases both birth spacing and the likelihood of a son. 
Using the four rounds of India's National Family and Health Surveys, I show that birth 
intervals increased substantially over the last four decades, with the most significant
increases among women most likely to use sex selection.
Specifically, well-educated women with no boys now have significantly longer birth
intervals, and more male-biased sex ratios, than similar women with boys. 
Women with no education still follow the standard pattern of short average spacing when 
they have girls and little evidence of sex selection, with medium-educated women showing 
mixed results.
Furthermore, the traditional pattern of longer average spacing with sons appears to arise 
not from fewer very short birth intervals, but rather from the upper end of the distribution.
Finally, northern and western India are responsible for most of the spacing pattern 
reversal, although even the south experienced substantially increased intervals from
sex selection.

@@

Finally, how are the changes in birth intervals distributed geographically?
Given the cultural differences within India, it is unlikely that the increasing 
access to sex selection will have had the same effects throughout \citep{retherford03b}.
I, therefore, examine how birth intervals have changed across four regions.

@@

With a country as large as India, it is natural to expect variation in both fertility
behavior, spacing patterns, and the degree of son preference.
Although the regional results confirm this, the differences are less apparent than one would
expect given the prior research.
The ``North'' and the ``West'' regions have relatively similar spacing patterns, both
the result of rapidly falling fertility and substantial use of sex selection.
The exception is that the rural ``North'' still have higher fertility and
consequently less use of sex selection.
Even the ``South,'' otherwise considered to have the least son preference, has 
seen a substantial increase in the use of sex selection and associated changes 
in the spacing patterns.
Finally, fertility has declined fastest in the ``East'' region, but this has not 
translated into the use of sex selection.

@@

\section{Results by Region}

\vspace*{-0.51cm}

\input{../tables/bootstrap_duration_avg_sex_ratio_high_r1.tex}

\input{../tables/bootstrap_duration_avg_sex_ratio_high_r2.tex}

\input{../tables/bootstrap_duration_avg_sex_ratio_high_r3.tex}

\input{../tables/bootstrap_duration_avg_sex_ratio_high_r4.tex}

\input{../tables/bootstrap_duration_p25_p75_high_r1.tex}

\input{../tables/bootstrap_duration_p25_p75_high_r2.tex}

\input{../tables/bootstrap_duration_p25_p75_high_r3.tex}

\input{../tables/bootstrap_duration_p25_p75_high_r4.tex}

>>>>

\date{December 2018}

@@

% Demography abstract
\noindent 
Strong son preference is typically associated with shorter birth spacing in the absence of 
sons, but access to sex selection has the potential to reverse this pattern because each 
abortion extends spacing by six to twelve months. 
I introduce an empirical method that simultaneously accounts for how sex selection 
increases both birth spacing and the likelihood of a son. 
Using the four rounds of India's National Family and Health Surveys, I show that birth 
intervals increased substantially over the last four decades, with the most significant
increases among women most likely to use sex selection.
Specifically, well-educated women with no boys now have significantly longer birth
intervals, and more male-biased sex ratios, than similar women with boys. 
Women with no education still follow the standard pattern of short average spacing when 
they have girls and little evidence of sex selection, with medium-educated women showing 
mixed results.
Furthermore, the traditional pattern of longer average spacing with sons appears to arise 
not from fewer very short birth intervals, but rather from the upper end of the distribution.

@@

@@

@@
